---
title: "Homework 2"

author: "Jessica Temporal 7547611"

date: "November 10, 2016"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    keep_tex: yes
  html_document:
    toc: no
---
\newpage

## 1. Read the provided text file into R, making sure to account for headers. This is a truncated cDNA array expression file that has only the Cy5 and Cy3 foreground and background values for 5 separate arrays. The numbers in the suffix of the names are time points (though not necessary for our purposes). (2.5 pts)
```{r}
file <- 'five.txt'
cdna <- read.table(file, header = T)
```

## 2. Load the sma library and the MouseArray data file (with data()). (2.5 pts)
```{r}
library(sma)
data(MouseArray)
```

## 3. Using list commands, turn the five_arrays matrix file into the list object that is similar to the mouse.data example.  See hints below. (10 pts)
```{r}

```

## 4. Now create a plot of both un-normalized and lowess normalized data for chip #5 (image.id argument) using the plot.mva function.  Make sure to use a par command to put both plots on the same page.  Title both plots. For the layout argument in plot.mva(), use the mouse.setup file. (15 pts)
```{r}

```

## 5. How do the 2 plots differ? What has lowess normalization done to the distribution of expression values? (5 pts)
```{r}

```