---
title: "Lab2"

subtitle: "Data visualization"

author: "Jessica Temporal 7547611"

date: "August 27, 2016"

output:
  pdf_document:
    toc: yes
    toc_depth: 3
  html_document:
    toc: no
---
\newpage

### 1. Use the Spellman yeast cell cycle dataset (spellman.txt).
```{r}
file <- "spellman.txt"
```

### 2. a) Read into R (Hint: using the read.table() function with a “header” argument is one method to do this).
```{r}
spellman_data <- read.table(file, header = T)
```

### 2. b) Set the row names to the first column, then remove this first column.
```{r}
rownames(spellman_data) <- spellman_data$row.names
spellman_data$row.names <- NULL
```

### 3. a) Look at the dimensions of the data frame and make sure that there are 6,178 genes and 77 arrays/sample.
```{r}

```

### 3. b) Isolate only the cdc15 experiment (samples 23-46), pick a gene with some missing values (I use gene #2/YAL002W in the solutions), and impute with the row mean (save as something).
```{r}

```

### 4. Look up the functions for boxplot and hist and plot the gene. Color the plots red and title them. Make sure that the vector is numeric (as.numeric).
```{r}

```

### 5. Generate a profile plot of the same gene. Title the plot. Use lwd in the plot command (lwd=line width).
```{r}

```
